EDA

### 2018-08-28 contest/eda/eda.Rmd
More EDA and thoughts

>>>>

```
```{r}
## Moving to boxplots
g2 <- ggplot(data = gs,
             aes(x = tournament, y= minutes,
                            group = tournament, col = tournament)) +
    geom_boxplot(size = 1)  + facet_grid(~n_sets)
g2

```
It appears Wimbledon has the shortest matches.
	## Retirements by court?

```{r}
## More boxplots
g2 <- ggplot(data = gs,
             aes(x = winner_ioc,
                            group = tournament, fill = tournament)) +
    geom_bar(aes(y=..prop..), size = 1)  + facet_grid(~tournament) + 
    theme(axis.text.x = element_text(angle = 90, hjust = 1)) + coord_flip()
g2

## RG has least amount of double faults
```

+ Find games won and lost
+ Find service games won/lost
+ Look at retirements by court
+ Look at wins by country by court
+ Find number of tiebreaks by court
+ Need to normalize wins by country by n_players in tournament (but both are interesting)
+ Look at gs point by point
+ Need to get French Open 2018 results
+ Get Women's data and combine it
+ Look atGS_point_by_point.  Is it complete?  Is it complete for rafa, serena, fed?
+ Facet by round
+ Do above but instead predict winner games, or winner sets, loser games, or loser sets
+ get hex colors of GS
